High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-06-28 inst/manuscript/manuscript.tex
Methods first section revised, including fig 1

%\begin{center}
This paper is a non-peer reviewed preprint submitted to EarthArXiv. It
will be periodically updated as it is revised, including information on
its peer review status.
%\end{center}

@@

Amidst all the challenges posed by global change, a particular concern
is how agricultural systems will adapt to meet humanity's growing food
demands, and the impacts that transforming and expanding food systems
will have on societies, economies, and the environment (Searchinger et
al. 2019). Significant efforts are being made to address the various
aspects of this challenge, including work on diagnosing and closing
yield gaps (Lobell et al. 2009, e.g. Licker et al. 2010, Mueller et al.
2012), expanding and commercializing production (Morris and Byerlee
2009), and to understand (Rulli and D'Odorico 2014, Kehoe et al. 2017,
Davis et al. 2020) and mitigate (Estes et al. 2016b) agriculture's
ecological impacts. Answering many of the questions these efforts seek
to address depends on reliable data that describes the location and
characteristics of cropland (Fritz et al. 2015), and how these are
changing over time. Unfortunately, the data that do exist are in many
places inaccurate. Existing estimates of how much global cropland there
is tend to vary widely, and they often disagree about where cropland is
located (e.g. Fritz et al. 2011, 2013). Such errors can propagate in
subsequent analyses that rely on cropland data as inputs, resulting in
potentially misleading answers (Estes et al. 2018). Beyond cropland
distributions, few data are available on key cropland characteristics
such as field size, an important variable needed to estimate yield and
other key food security variables (Carletto et al. 2015), and as an
indicator of farm size (Levin 2006, Samberg et al. 2016), a critical
component of rural livelihoods given increasing population densities and
longstanding debates about the relationship between farm size and
productivity (Feder 1985, Carletto et al. 2013, Desiere and Jolliffe
2018).

These informational inadequacies are due to the fact that cropland data
in much of the world are derived from remotely sensed landcover maps,
which can be notoriously high in error, particularly over regions such
as Africa (Fritz et al. 2010, Estes et al. 2018), where agricultural
changes will be largest and the need for accurate baseline data is thus
greatest (Searchinger et al. 2015, Estes et al. 2016b, Bullock et al.
2021). Cropland mapping over Africa is difficult for several reasons.
The primary reason relates to the characteristics of the continent's
smallholder-dominated croplands, where half of all fields are smaller
than 1 ha (Lesiv et al. 2019). This size is small relative to the 30-250
m resolution of the sensors typically used in many landcover mapping
efforts (e.g. Chen et al. 2015, Sulla-Menashe et al. 2019), which
results in errors due to mixed pixels and aspects of the modifiable area
unit problem (Openshaw and Taylor 1979). In the latter case, the pixel's
shape may be poorly matched to that of cropland, and is too coarse to
aggregate to approximate that shape at the characteristic scales of crop
fields (Dark and Bram 2007, Estes et al. 2018). On top of the matter of
scale is 1) high intra-class variability of the cropland class,
compounded by the fact that these particular croplands can be heavily
intergraded with surrounding vegetation (Debats et al. 2016, Estes et
al. 2016a), and 2) the substantial temporal variability within
croplands, both within and between seasons. These latter two aspects
pose challenges for the classification algorithms that are applied to
the imagery.

These problems arising from cropland characteristics are increasingly
being addressed due to technological advances. Recent advances in
satellite technology have increased the coverage of high (\textless5 m)
or near-high (10 m) resolution imagery with weekly to near-daily return
intervals (Drusch et al. 2012, McCabe et al. 2017). This high spatial
\emph{and} temporal resolution addresses the sensor-field scale
mismatch, and more effectively captures the intra-seasonal dynamics of
cropland, which helps classifiers distinguish cropland from surrounding
cover types (Debats et al. 2016, Defourny et al. 2019). On top of this,
advances in cloud computing (Gorelick et al. 2017), the opening of image
archives (Wulder et al. 2016), and next generation machine learning
approaches (Zhu et al. 2017, Maxwell et al. 2018) are placing large
volumes of these moderate to near-high resolution imagery together with
the computational and algorithmic resources necessary to classify them
at scale. These capabilities are aleady being used to create a new
generation of higher resolution (10-30 m) cropland and landcover maps
for Africa and other regions (Xiong et al. 2017, Lesiv et al. 2017, ESA
n.d.).

Despite these advances, the highest resolution (\textless5 m) image
sources are still not used to map cropland over very large extents,
presumably because they are commercial and relatively high cost to
acquire, in addition to the greater computational demands. As such, map
accuracy can still be a challenge, particular for User's accuracy, which
ranges between 46 and 76\% for the cropland class (Xiong et al. 2017,
e.g. Lesiv et al. 2017).

Accuracy may also suffer due to error-inducing factors that are becoming
somewhat more pronounced as a consequence of these technology advances,
particularly with respect to algorithms. Advances in machine learning
are helping to greatly improve classification skill, but these
algorithms generally require large, high-quality training datasets
(Maxwell et al. 2018, Ma et al. 2019, Elmes et al. 2020). To satisfy
this need for more training (and reference) samples, map-makers
increasingly rely on visual interpretation of high resolution satellite
or aerial imagery to collect training (or validation) samples (Chen et
al. 2015, e.g. Xiong et al. 2017, Stehman and Foody 2019). Several
web-based platforms have been developed to facilitate such efforts,
which provide convenient and highly scalable tools for training data
collection (Fritz et al. 2012, Estes et al. 2016a, e.g. Bey et al.
2016). Visually interpreted training labels present two particular
problems. The first is that such labels have inevitable interpretation
errors that can vary substantially according to the skill of the
interpreter (Estes et al. 2016a, Waldner et al. 2019). These errors are
typically not accounted for in reported accuracy metrics, despite the
fact that they can introduce substantial error into the resulting maps
and subsequent analyses (Estes et al. 2018, Elmes et al. 2020). The
second problem is that visual interpretation depends on high resolution
imagery (\textless5 m), as lower resolutions make it difficult for a
human analyst to discern cropland. Typically the only practical source
for such imagery are ``virtual globe'' basemaps provided by Microsoft
and Google, which are composed of mosaics of various high resolution
satellite and aerial images that typically span 3-5 years of time within
a single country (Lesiv et al. 2018). This within-mosaic temporal
variation can set up a temporal mismatch between the imagery being
interpreted and the imagery being classified, which is usually from a
different source (e.g.~Landsat, Sentinel; Xiong et al. (2017)). If a
land change occurs in the interval between the two image sets (e.g.~a
new field was created), this can introduce error into the training data
that is then passed on to the classifier. This source of error may be
elevated in smallholder-dominated systems in the tropics, where swidden
practices are common (Van Vliet et al. 2013), or in rapidly developing
agricultural frontiers (Zeng et al. 2018).

Improving the accuracy of cropland maps over smallholder-dominated
systems thus requires an approach that meets three requirements. First,
it should be based on high spatial and temporal resolution imagery, to
be able to capture the fine grain and temporal variability of
smallholders' fields. Second, an algorithm with suitable skill for
classifying these images must be selected, and combined with the
computational resources needed to process large imagery volumes. Third,
a method for collecting large volumes of high quality training and
validation data based on image interpretation is essential. This method
should quantify and minimize the errors associated with image
interpretation. It should also ensure that labels are collected either
from the same imagery that is being classified, or from contemporanous
imagery, in order to reduce errors introduced by land change processes.

We describe here a cropland mapping system that follows these
requirements, with an emphasis on delineating field boundaries. The
first requirement is enabled by the recent availability of CubeSat data
that provides 3-4 m resolution imagery over large areas at near daily
intervals (McCabe et al. 2017). Although these data, currently collected
by Planet's CubeSat fleet, are of lower spectral depth and quality than
Landsat, Sentinel, or Worldview imagery, they enable country to
continental scale image mosaics to be created for multiple periods
during the crop growing calendars, and capturing the intra-annual
variability can be more important for classifying cropland than spectral
depth (Debats et al. 2016). This daily revisit capacity is also
important for developing seasonal composites in cloudy regions, where
satellites with longer return intervals may fail. Lastly, although this
imagery being up to \textasciitilde16 times coarser than much of Bing or
Google imagery, it is sufficiently resolved for humans to discern most
fields (Fourie 2009, e.g.~see Estes et al. 2018). This allows labels to
be generated on the same imagery processed by the classifier, thereby
addressing one of the two needs related to training data (requirement
3).

The second requirement is addressed by a computer vision/machine
learning classifer that is effective for classifying smallholder
croplands (Debats et al. 2016), re-engineered to run on high
performance, cloud-based computing clusters with a simplified feature
set, and following recommended practices for controlling for and
measuring the errors that occur when training machine learning models
for remote sensing applications (Elmes et al. 2020). The classifier is
tightly coupled to a front-end platform for collecting label data, which
includes rigorous accuracy assessment protocols and a novel approach for
merging multiple maps into consensus labels, thereby minimizing image
interpretation error (Estes et al. 2016a, Elmes et al. 2020). The
training and machine learning components are combined within an active
learning framework, wherein the machine learning process assesses
classification uncertainty in unlabelled areas after a training step,
and selects sites from areas of highest uncertainty for additional
labelling (Cohn et al. 1994, Tuia et al. 2011). Our framework automates
this interactive approach to label selection, which is effective in
boosting the performance of classification models while reducing the
overall number of training samples required to achieve a given level of
performance (Debats et al. 2017, e.g. Hamrouni et al. 2021). Finally, an
unsupervised segmentation step is applied to the imagery and merged with
the pixel-wise classifications from the machine learning process,
resulting in a vectorized field boundary map that provides important
information on field geometry.

We demonstrate this approach to map cropland in Ghana, a country where
smallholder farming predominates, and which has a broad mix of climates
and agricultural systems, including large areas where shifting
agriculture is practiced (Samberg et al. 2016, Kansanga et al. 2019).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{system-overview}{%
\subsection{System overview}\label{system-overview}}

The mapping system design has four primary components focused on 1)
image acquisition and compositing, 2) training and validation data
collection, 3) image classification, and 4) segmentation. The first
component is applied as a once-off step to generate an image catalog
covering the mapping geography. The second component provides tools for
labelling imagery, and controls an interactive model training and
classification (component 3) pipeline that produces a map of cropland
probabilities for each image pixel (Figure \ref{fig:systemoverview}).
The final segmentation step (component 4) is then initiated and applied
to both the input image catalog and the posterior probability maps,
resulting in vectorized field boundaries. Each system component
comprises an individual software module designed to be implemented on
cloud computing architecture, and available on a GitHub repository (see
data and software availability section for details).

@@

\hypertarget{system-components}{%
\subsection{System components}\label{system-components}}

\hypertarget{image-compositing}{%
\subsubsection{Image compositing}\label{image-compositing}}

@@

Where \(\theta\) represents the true cover type of a pixel (field or not
field), \emph{D} is the label assigned to that pixel by a labeller, and
\(W_i\) is an individual labeller. P(\(\theta\)\textbar D) is therefore
the probability that the actual cover type is what the labellers who
mapped it says it is, while P(W\(_i\)\textbar D) is an individual
labeller's average score over all the accuracy assessment assignments
they have completed, and P(W\(\theta\)\textbar D, \emph{W\(_i\)}) is the
labeller's label for that pixel. This approach therefore uses the
overall accuracy of each labeller to weight their labels when combined
with those made by other labellers' for the same pixel (see SI for
further details). As a further measure of confidence in the final
consensus label, its average Bayesian Risk can be calculated (see SI).
This measure ranges between 0 and 1, with 0 indicating full agreement
between labellers for all pixels (n = 40000) in the label, and 1
indicating complete disagreement.

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-ZhuDeeplearningremote2017}{}%
Zhu, X. X., D. Tuia, L. Mou, G.-S. Xia, L. Zhang, F. Xu, and F.
Fraundorfer. 2017. Deep learning in remote sensing: A review. IEEE
Geoscience and Remote Sensing Magazine 5:8--36.

>>>>

%\begin{center}
This pre-print not yet undergone peer review. It has been submitted to
the \emph{Frontiers in Artificial Intelligence}. This version will be
updated as it is revised, and the final published version will be
accessible through its DOI link.
%\end{center}

@@

Amidst all the challenges posed by global change, a particular concern
is how agricultural systems will adapt to meet humanity's growing food
demands, and the impacts that transforming and expanding food systems
will have on societies, economies, and the environment (Searchinger et
al. 2019). Significant efforts are being made to address the various
aspects of this challenge, including work on diagnosing and closing
yield gaps (Lobell et al. 2009, e.g. Licker et al. 2010, Mueller et al.
2012), expanding and commercializing production (Morris and Byerlee
2009), and to understand (Rulli and D'Odorico 2014, Kehoe et al. 2017,
Davis et al. 2020) and mitigate (Estes et al. 2016b) agriculture's
ecological impacts. Answering many of the questions these efforts seek
to address depends on reliable data that describes the location and
characteristics of cropland (Fritz et al. 2015), and how these are
changing over time, ideally on an annual basis, given the rapid pace of
change (Gibbs et al. 2010, Bullock et al. 2021). Unfortunately, the data
that do exist are in many places inaccurate and infrequently updated.
Existing estimates of how much global cropland there is tend to vary
widely, and they often disagree about where cropland is located (e.g.
Fritz et al. 2011, 2013). Such errors can propagate in subsequent
analyses that rely on cropland data as inputs, resulting in potentially
misleading answers (Estes et al. 2018). Beyond cropland distributions,
few data are available on key cropland characteristics such as field
size, an important variable needed to estimate yield and other key food
security variables (Carletto et al. 2015), and as an indicator of farm
size (Levin 2006, Samberg et al. 2016), a critical component of rural
livelihoods given increasing population densities and longstanding
debates about the relationship between farm size and productivity (Feder
1985, Carletto et al. 2013, Desiere and Jolliffe 2018).

These informational inadequacies are due to the fact that cropland data
in much of the world are derived from remotely sensed landcover maps,
which can be notoriously high in error, particularly over regions such
as Africa (Fritz et al. 2010, Estes et al. 2018), where agricultural
changes will be largest and the need for accurate baseline data is thus
greatest (Searchinger et al. 2015, Estes et al. 2016b, Bullock et al.
2021). Cropland mapping over Africa is difficult for several reasons.
The primary reason relates to the characteristics of the continent's
smallholder-dominated croplands, where half of all fields are smaller
than 1 ha (Lesiv et al. 2019). This size is small relative to the 30-250
m resolution of the sensors typically used in many landcover mapping
efforts (e.g. Chen et al. 2015, Sulla-Menashe et al. 2019), which
results in errors due to mixed pixels and aspects of the modifiable area
unit problem (Openshaw and Taylor 1979, Boschetti et al. 2004){]}. In
the latter case, the pixel's shape may be poorly matched to that of
cropland, and is too coarse to aggregate to approximate that shape at
the characteristic scales of crop fields (Dark and Bram 2007, Estes et
al. 2018). On top of the matter of scale is 1) high intra-class
variability of the cropland class, compounded by the fact that these
particular croplands can be heavily intergraded with surrounding
vegetation (Debats et al. 2016, Estes et al. 2016a), and 2) the
substantial temporal variability within croplands, both within and
between seasons. These latter two aspects pose challenges for the
classification algorithms that are applied to the imagery.

Recent technological advances are helping to overcome these challenges.
Chief among these are the growing numbers of satellites that collect
high (\textless5 m) to near-high (10 m) resolution imagery at sub-weekly
intervals (Drusch et al. 2012, McCabe et al. 2017). This high spatial
\emph{and} temporal resolution imagery addresses the sensor-field scale
mismatch, and more effectively captures the intra-seasonal dynamics of
cropland, which helps classifiers distinguish cropland from surrounding
cover types (Debats et al. 2016, Defourny et al. 2019). On top of this,
advances in cloud computing and the opening of satellite image archives
(Wulder et al. 2016), and next generation machine learning approaches
are placing large volumes of these moderate to near-high resolution
imagery together with the computational and algorithmic resources
necessary to classify them at scale (Gorelick et al. 2017). These
capabilities are already being used to create a new generation of higher
resolution (10-30 m) cropland and landcover maps for Africa and other
regions {[}ESA (n.d.); Lesiv et al. (2017); Xiong et al. (2017); (Zhang
et al. 2021){]}. However, the potential of the highest resolution
(\textless5 m) imagery to map cropland over very large extents
(e.g.~country scales) has yet to be realized, presumably because these
data are commercial and relatively expensive, and require significant
computational resource to process.

Beyond the imagery and computational gains, machine learning algorithms
are rapidly advancing, providing large gains in classification
performance (Maxwell et al. 2018, Ma et al. 2019). However, the ability
to take advantage of these gains is often limited by newer models' need
for large training datasets, which are typically unavailable, hard to
collect, or contain numerous errors in developing regions (Ma et al.
2019, Elmes et al. 2020, Burke et al. 2021). To build sufficient samples
for training cropland mapping models, as well as the reference data
needed to objectively assess their performance (we refer collectively to
both sample types as ``labels,'' distinguishing between each type where
needed), map-makers rely heavily on visual interpretation of high
resolution satellite or aerial imagery (Chen et al. 2015, e.g. Xiong et
al. 2017, Stehman and Foody 2019), as it is impractical and expensive to
collect these data in the field over large areas, particularly on an
ongoing basis. Several web-based platforms have been developed to
facilitate such efforts, which provide convenient and highly scalable
tools for training data collection (Fritz et al. 2012, Estes et al.
2016a, e.g. Bey et al. 2016). Visually interpreted labels present two
particular problems. The first is that they inevitably contain errors of
interpretation that can vary substantially according to the skill of the
labeller, particularly over complex croplands with small field sizes
(Estes et al. 2016a, Waldner et al. 2019). The second problem is that
visual interpretation depends on high resolution imagery (\textless5 m),
as field boundaries become increasingly difficult to discern as image
resolution decreases. Typically the only practical source of high
resolution imagery is ``virtual globe'' basemaps (e.g.~Bing or Google
Maps), which are composed of mosaics of various high resolution
satellite and aerial images that typically span 3-5 years of time within
a single country (Lesiv et al. 2018). This within-mosaic temporal
variation can set up a temporal mismatch between the imagery being
interpreted and the imagery being classified, which is usually from a
different source (e.g.~Landsat, Sentinel; Xiong et al. (2017)). If a
land change occurs in the interval between the two image sets (e.g.~a
new field was created), the label, even if accurately drawn, introduces
error into the classifier. This source of error may be elevated in
tropical smallholder systems, where swidden agricultural is common (Van
Vliet et al. 2013), or in rapidly developing agricultural frontiers
(Zeng et al. 2018). Despite the high potential for label error, they are
typically not accounted for during model training and map accuracy
assessment, resulting not only in the potential for maps to be misused
or misinterpreted in subsequent analyses, but in missed opportunities to
improve model performance (Estes et al. 2018, Stehman and Foody 2019,
Elmes et al. 2020).

Taking into consideration the advances and remaining limitations
described above, the ability to map smallholder-dominated croplands can
be further improved by 1) more fully exploiting the profusion of high
frequency, high resolution imagery provided by CubeSats (McCabe et al.
2017), and 2) by implementing methods that improve the ability to
collect and minimize errors in image-interpreted labels. We developed a
mapping approach that focuses on these two sources of improvement. Our
approach uses PlanetScope imagery collected by Planet's fleet of Dove
satellite, which provides 3-4 m resolution imagery over large areas at
near daily intervals (McCabe et al. 2017, PlanetTeam 2018), at
relatively low to no cost for academic
research\footnote{www.planet.com/markets/education-and-research/} and
non-commercial, sustainability-oriented
applications\footnote{assets.planet.com/docs/Planet\_ParticipantLicenseAgreement\_NICFI.pdf}.
Although these data are of lower spectral depth and, in some cases,
quality, than Landsat, Sentinel, or Worldview imagery, their daily
revisit enables country- to continent-scale image mosaics to be created
for multiple periods during a single agricultural year, even over the
cloudiest forest regions where it is hard to successfully construct
cloud-free composites from optical imagery with return intervals (even
by a few days). This ability to capture intra-annual variability can be
more important for classifying cropland than spectral depth (Debats et
al. 2016). Beyond the frequency, PlanetScope's 3.7 m
resolution--although substantially coarser the 0.5-1 m available in most
areas covered by virtual globes--is sufficiently resolved for humans to
discern small fields under many conditions (Fourie 2009, e.g.~see Estes
et al. 2018). This allows labels to be made using the same imagery that
is classified, which helps to minimize label error. To further reduce
label noise, we developed a platform that includes rigorous label
accuracy assessment protocols and a novel approach for creating
consensus labels, which helps reduce mistakes made by individual
labellers (Estes et al. 2016a, Elmes et al. 2020). We couple the
labelling platform with a machine learning model inside an active
learning (Cohn et al. 1994, Tuia et al. 2011) framework, in which model
training is done iteratively and interactively, wherein the model's
prediction uncertainty over unlabelled areas is assessed after each
training step, and a sample of the most uncertain sites is selected for
additional labelling (Cohn et al. 1994, Tuia et al. 2011). This approach
helps boost the performance of the classifier while reducing the overall
number of labels required to achieve a given level of performance
(Debats et al. 2017, e.g. Hamrouni et al. 2021). Finally, an
unsupervised segmentation step is applied to convert pixel-wise cropland
predictions into vectorized maps of individual field boundaries.

Here we use this approach to create a high resolution, country-scale map
of crop field boundaries in Ghana, a country where smallholder farming
predominates, and which has a broad mix of climates and agricultural
systems, including large areas where shifting agriculture is practiced
(Samberg et al. 2016, Kansanga et al. 2019). The map we develop
represents a single agricultural year (2018-2019), as opposed to a
multi-year composite, thereby demonstrating a capacity for annual, high
resolution maps that can be used to monitor rapidly evolving small-scale
agricultural systems, including key characteristics such as field size.
In addition to presenting one of the most spatially extensive
agricultural applications of CubeSats to date, we provide a new
technique for converting daily imagery into seasonal composites, and
show how best practices for model training and label collection can be
applied to improve map accuracy (Elmes et al. 2020).

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

The cropland mapping approach we developed is comprised of four primary
components (Figure \ref{fig:systemoverview}) that were developed using
open source software, and is designed to run in a cloud computing
environment. The first component collects daily PlanetScope imagery for
a period of several months over a particular mapping geography, and
converts these into cloud-free seasonal composites. The second component
is a custom-built platform that a provides a set tools for labelling the
PlanetScope composites, and built-in procedures for assessing and
minimizing label error. This platform interacts with the third
component, a machine learning process running in Apache Spark, which
includes a routine for 1) selecting new training sites based on their
prediction uncertainty, and 2) returning these to the labelling platform
for labeling. This interaction, which represents active learning (Cohn
et al. 1994, Tuia et al. 2011), repeats until a model performance
threshold is reached. The fourth and final component is a segmentation
process that is applied to the seasonal image composites to segment the
entire image, and then merged with the pixel-wise probability maps
generated by active learning to identify the segments corresponding to
croplands, resulting in a final vectorized field boundaries. Each system
component is available on an open repository (see data and software
availability section for details).

@@

\hypertarget{image-compositing}{%
\subsection{Image compositing}\label{image-compositing}}

@@

Where \(\theta\) represents the true cover type of a pixel (field or not
field), \emph{D} is the label assigned to that pixel by a labeller, and
\(W_i\) is an individual labeller. P(\(\theta\)\textbar D) is therefore
the probability that the actual cover type is what the labellers who
mapped it says it is, while P(W\(_i\)\textbar D) is an individual
labeller's average score over all the accuracy assessment assignments
they have completed, and P(W\(\theta\)\textbar D, \emph{W}\(_i\)) is the
labeller's label for that pixel. This approach therefore uses the
overall accuracy of each labeller to weight their labels when combined
with those made by other labellers' for the same pixel (see SI for
further details). As a further measure of confidence in the final
consensus label, its average Bayesian Risk can be calculated (see SI).
This measure ranges between 0 and 1, with 0 indicating full agreement
between labellers for all pixels (n = 40000) in the label, and 1
indicating complete disagreement.

@@

\leavevmode\hypertarget{ref-boschettiAnalysisConflictOmission2004}{}%
Boschetti, L., S. P. Flasse, and P. A. Brivio. 2004. Analysis of the
conflict between omission and commission in low spatial resolution
dichotomic thematic products: {The Pareto Boundary}. Remote Sensing of
Environment 91:280--292.

@@

\leavevmode\hypertarget{ref-burkeUsingSatelliteImagery2021}{}%
Burke, M., A. Driscoll, D. B. Lobell, and S. Ermon. 2021. Using
satellite imagery to understand and promote sustainable development.
Science 371.

@@

\leavevmode\hypertarget{ref-GibbsTropicalforestswere2010}{}%
Gibbs, H. K., A. S. Ruesch, F. Achard, M. K. Clayton, P. Holmgren, N.
Ramankutty, and J. A. Foley. 2010. Tropical forests were the primary
sources of new agricultural land in the 1980s and 1990s. Proceedings of
the National Academy of Sciences 107:16732--16737.

@@

\leavevmode\hypertarget{ref-zhangGLCFCS30Global2021a}{}%
Zhang, X., L. Liu, X. Chen, Y. Gao, S. Xie, and J. Mi. 2021.
{GLC}\_{FCS30}: Global land-cover product with fine classification
system at 30 m using time-series {Landsat} imagery. Earth System Science
Data 13:2753--2776.

@@
